Proposal: DINO Methods for Style Transfer

### 2022-03-04 Proposal.tex
some typos and refactorings

For the purpose of DINO training we add a teacher content encoder and a teacher style encoder. Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images. We then add the loss from the standard style transfer and the cross entropy loss between the teacher encodings and and the student encodings. This forces the students to learn distillations of the original images. We expect this to work better for the style encoder, because style is a global property of an image, so we may only apply this method for the style encoder.

@@

This method is similar to the previous expect instead of taking the cross entropy between the encodings we take apply the decoder transformer to the encodings from the teacher encoders, to yield a new image. We then use the distance between the teacher image and the student image in our loss. The precise distance metric used here is to be determined through experimentation. This will allow the encoders to distill the important pieces of the stylized image. This method may suffer from being very expensive to train. We also may only apply this to the style encoder.

>>>>

For the purpose of DINO training we add a teacher content encoder and a teacher style encoder. Now, as in the DINO method, the content and style transformers are given distorted versions of the images (possibly only cropped and flipped to avoid abstracting the incorrect style characteristics), and the teachers are given the unmodified images. We then add together the loss from the standard style transfer and the cross entropy loss between the teacher encodings and the student encodings. This forces the students to learn distillations of the original images. We expect this to work better for the style encoder, because style is a global property of an image, so we may only apply this method for the style encoder.

@@

This method is similar to the previous, except that instead of taking the cross entropy between the encodings, we take apply the decoder transformer to the encodings from both the teacher and student encoders, which would yield a teacher image and a student image. We then use the distance between the teacher image and the student image in our loss. The precise distance metric used here is to be determined through experimentation. This will allow the encoders to distill the important pieces of the stylized image. This method may suffer from being very expensive to train. We also may only apply this to the style encoder.
